Open electronic signature software

### 2020-01-27 paper/main.tex
Update Law subsection, Cryptography outline

Advanced electronic signatures are a subset of electronic signatures that have to uniquely link and identify the signature author, be created in a way that is possible only by them and any changes to the signed document is detectable \cite{5}.
From the technical point of view, standards PAdES, XAdES and, CAdES specified by the ETSI comply with these requirements.

@@

Such right can be exercised, as far as we are concerned, to license the software under either proprietary or open-source license.
Proprietary meaning under exclusive legal right of the author, typically also confidential and distributed as a paid product.
Open-source meaning having its source code freely available, typically also distributed for free.

@@

Copyleft license, in general, requires the user to publish the modified work under the compatible (free) license.
Meaning forcing them to extend the rights they have received onto others and, in turn, somehow hindering use in software licensed under a different license and potential commercialization.
Popular example of such license is the GNU General Public License (GPL) and its derivatives like GNU Lesser GPL (LGPL) or GNU Affero GPL (AGPL).

@@

It is not uncommon to see hybrid licensing - licensing under more than one license with one being open-source and one proprietary.

@@

@@

\subsection{Asymmetric cryptography}

@@

@@

  \bibitem{1}
  \emph{§ 40 ods. 3 zákona č. 40/1964 Zb. občiansky zákonník}

@@

>>>>

Advanced electronic signatures are a subset of electronic signatures that have to uniquely link and identify the signature author, be created in a way that is possible only by them and any changes to the signed document is detectable \cite{5}.
From the technical point of view, standards PAdES, XAdES, and CAdES specified by the ETSI comply with these requirements.

@@

Such right can be exercised, as far as we are concerned, to license the software under either proprietary or open-source license.
Proprietary meaning under exclusive legal right of the author, typically also confidential and distributed as a paid product.
Open-source meaning having its source code freely available, typically also distributed for free and without any liability (the software is provided "as is").

@@

Copyleft license, in general, requires the user to publish the modified work under the compatible (free) license.
Meaning forcing them to extend the rights they have received onto others and, in turn, somehow hindering use in software licensed under a different license.
Popular example of such license is the GNU General Public License (GPL) and its derivatives like GNU Lesser GPL (LGPL) or GNU Affero GPL (AGPL).

@@

It is not uncommon to see hybrid licensing - licensing under more than one license, with one being typically open-source and one proprietary.
In this scenario, users can choose which license they want to use based on their needs.

@@

As we have already mentioned, software licenses can influence whether and how it can be used as a part of different software.
Both when we are using someone else's software and when someone else is using our software.
Generally speaking, the more open the license is, the higher the probability it will not stop adoption for legal reasons.
Various possible combinations can be seen in Figure 3, where greyed out options mean such combination is not possible unless a separate licensing agreement is reached with the copyright owner.

\obrazok{./figures/license-compatibility}{Schematic representation of license directionality.\cite{7}}

\newpage

@@

Previously mentioned standards PAdES, XAdES, and CAdES define how asymmetric cryptography, hashing, or timestamping should be used to comply with the standards.
We go over a few of these topics and why they are able to satisfy the requirements.

\subsection{Asymmetric encryption}

TODO: How it works.

TODO: How the private key is stored on the HSM, PKCS11 (be created in a way that is possible only by them).

TODO: Third party completing the trust chain (uniquely link and identify).

@@

TODO: How it works.

TODO: How it is used on the documents (guaranted that changes are detected).

\subsection{Timestamping}

TODO: How it works.

TODO: How it is used on the documents (parallels with the hand-written signature and date on the contract).

TODO: Long term validation.

\subsection{PAdES, XAdES, and CAdES}

TODO: Quick explanation of each.

TODO: How they can be used on a different file formats (table).

@@

  %  ------
  % Law
  %  ------
  \bibitem{1}
  \emph{§ 40 ods. 3 zákona č. 40/1964 Zb. občiansky zákonník}

@@

  %  ------
  % Article
  %  ------
  \bibitem{7}
  \osoba{Morin, A.}, et al. 2012. A Quick Guide to Software Licensing for the Scientist-Programmer. In: \emph{PLoS computational biology} [online]. Volume 8, issue 7 [cit. 2020-01-27]. e1002598. Available at: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1002598}
